Marzuki Nooranas

### 2023-10-20 index.qmd
Update
update

---
title: ""
---

@@

![](src/images/namelogo.png)

@@

```{=html}
<style>
    .tiktok-container {
        display: flex;
        justify-content: center;
        align-items: center;
        gap: 20px; /* Adjust for spacing between the embeds */
    }

    .tiktok-embed {
        width: 50%; /* Adjust based on your desired width */
        max-width: none;
    }
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">

@@

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
# **My Past Work**

>>>>

---
title: "Marzuki Nooranas"
---

@@

@@

```{=html}
<style>
.tiktok-container {
  display: flex;
  flex-wrap: wrap;
  justify-content: center;
}

.tiktok-embed {
  max-width: 100%;
  flex: 1 1 300px;
}

@media screen and (max-width: 600px) {
  .tiktok-embed {
    min-width: auto;
  }
}
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">

@@

# **My Past Work**
